%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
%
%Original template was downloaded from:
%http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% And
% Santosh Patil (https://github.com/sk4x0r)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt, a4paper]{deedy-resume}
\usepackage{setspace}
\usepackage{parallel,enumitem}
\newcommand\textbox[1]{%
  \parbox{\textwidth}{#1}%
}

\begin{document}
\leavevmode \\
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\lastupdated % Print the Last Updated text at the top right
\namesection{}{Santosh Patil}{ % Your name
\href{mailto:santoshpatil@outlook.com}{santoshpatil@outlook.com} \\ +91-8095-876816 % Your contact information
}
\section{Summary}
\textbox{
\-\ \-\ \-\ \-\ Computer Science graduate from \textbf{IIT Bombay} with interest in numbers, algorithms and artificial intelligence. Currently solving \textbf{scalability} problems around payment system at \textbf{Flipkart}. Fascinated by but still noob in \textbf{statistics} and \textbf{machine learning}. Seeking an opportunity in startup like environment where I can solve challenging problems and make the world a better place to live.\\}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0.4pt}}
%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.29\textwidth} % The left column takes up 29% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------
\setstretch{1.2}
\section{Education}

\subsection{Indian Institute of Technology, Bombay}

\descript{M.Tech in Computer Science and Engineering}
\location{July 2012 - June 2014 \\ CGPA: 8.14 / 10}

\sectionspace % Some whitespace after the section

\subsection{Government College of Engineering, Amravati}
\descript{B.Tech in Computer Science and Engineering}
\location{July 2006 - May 2010 \\ CGPA: 6.76 / 10}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links}
\textbf{LinkedIn:}//\href{https://www.linkedin.com/in/sk4x0r}{sk4x0r} \\
\textbf{Github:}//\href{https://github.com/sk4x0r}{sk4x0r} \\
\textbf{StackOverflow:}//\href{http://stackoverflow.com/users/717417}{santosh-patil} \\
\textbf{Goodreads:}//\href{http://goodreads.com/santoshpatil}{santoshpatil}

\sectionspace

%------------------------------------------------
% Technologies
%------------------------------------------------

\section{Technologies}
\location{Proficient:}
Java \textbullet{} MySQL \textbullet{} Redis
\\
\location{Intermediate:}
Python \textbullet{} C/C++ 
\\
\location{Exploring:}
R \textbullet{} Hadoop \textbullet{} Hive \textbullet{} Go
\sectionspace
\section{Tools}
Git \textbullet{} Maven \textbullet{} Latex

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill \vrule \hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.68\textwidth} % The right column takes up 68% of the text width of the page
\setstretch{1.1}
%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}
\runsubsection{Flipkart}
\descript{| Software Development Engineer}

\location{July 2014 – till date | Bangalore, IN}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
At Flipkart, I have been working on solving scalability problems in \textbf{payment systems}. The work focuses around \textbf{scaling} the existing payment systems to handle heavy load. For the last `Big Billion Day' sale, system was scaled to handle \textbf{10X} load of the existing peak capacity.
I have also worked on abstracting \textbf{sharding} at application level to achieve high availability as well as high throughput via \textbf{horizontal scaling}.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{NVIDIA}
\descript{| GPU QA Engineer}

\location{July 2010 – March 2011 | Pune, IN}
\vspace{\topsep}
At Nvidia, I was working on \textbf{quality assurance} of \textbf{GPU drivers} to be released for Laptops. The responsibilities included: \\~\\
\begin{tightitemize}
\item Executing hardware and software test plans for functional, stability and performance \textbf{testing}.
\item Capturing and \textbf{debugging} issues and work alongside development teams to fix issues.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------
\section{Academic Project}
\runsubsection{Solving Boolean Satisfiability Problem Using Orthonormal Expansion}
\descript{| Master's Thesis Project}
\location{June 2013 – June 2014 | IIT Bombay, IN}
\vspace{\topsep}
Worked with \textbf{\href{https://www.ee.iitb.ac.in/web/faculty/homepage/vrs}{Prof V. R. Sule}} to develop and implement a new approach to solve \textbf{boolean satisfiability} problem (SAT). The approach uses \textbf{orthonormal expansion} and \textbf{parallel processing} to solve SAT.

\sectionspace % Some whitespace after the section


%------------------------------------------------

% Scholastic Achievements
%------------------------------------------------

\section{Scholastic Achievements} 
\vspace{\topsep}
\begin{tightitemize}
\item Stood \textbf{34th among 156,000} students who appeared for the \textbf{GATE} (Graduate Aptitude Test in Engineering) \textbf{2012}
\item Received the prestigious \textbf{NTS} (National Talent Search) Scholarship award in \textbf{2004}. Only top 1000 students across the nation were awarded the scholarship.
\item Was awarded Maharashtra Talent Search Scholarship in 2002 and 2003.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
\end{document}